\documentclass[letter]{res}

\setlength{\textheight}{9.5in}
%\usepackage{fontspec}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=25mm,
 top=17mm,
 bottom=17mm,
 bindingoffset=0mm
 }\usepackage{fontenc}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage[colorinlistoftodos]{todonotes}
%\setmainfont[Mapping=tex-text]{Linux Libertine O}


\begin{document}

\name{Julian Mentasti Meza\\[14pt]}
\address{ (778)-882-3453 \\}
\address{
  \texttt{julian@mentasti.net}\\ } 
\begin{resume}
  \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}

\section{Education}
{\sl Bachelors of Science} - Combined Major in Computer Science and Statistics \hfill Expected: May 2020\\
University of British Columbia,  Vancouver, CA
  \vspace{-2mm}
  
International Baccalaureate Bilingual Diploma \hfill August 2015 – June 2017\\
Greengates School, Mexico City, MX
\section{Relevant Coursework}
  {\sl Computer Science}: Algorithms and Data Structures, Software Construction and Models of Computation.
  {\sl Mathematics}: Matrix Algebra.

\section{Experience}
UBC Orbit - Satellite Design Team| Vancouver, CA \newline
 - {\sl Payload Developer} \hfill January 2018 – Present\\
 Working to deploy a remote sensing satellite capable of identifying wildfires and forest loss by using machine learning models.\\
 \vspace{-2mm}
 \begin{itemize}
 \item Deployed a linear deblurring algorithm using the Lucy-Richardson algorithm.
 \item Created a Forrest fire identifier by inverting spectral bands and haar cascades. 
 \item Created a system status service to monitor Payload's computing system. 
 \end{itemize}
   \vspace{-2mm}
   
\section{Skills}
{\sl Programming Languages:}  Java, C++, and Python\\
{\sl Operating Systems:} Linux/Unix system, Windows \\ 
{\sl Software:} NI Multisim, SPICE software,  \LaTeX \\ 
{\sl Laboratory:}  oscilloscope, logic analyzer, signal generator, solder, and multimeter \\
 \vspace{-2mm}

\section{Projects}
Raspberry Pi Robot \newline - {\sl Individual} \\
\begin{itemize}
  \vspace{-2mm}
 \item Using a Raspberry Pi to construct a remote control robot.
 \item Camera module connection for live streaming robot vision back to monitor.
 \item Developed Python code to control robot motions and camera module.
\end{itemize}
3pi Robot \newline - {\sl Group Project}\\
\begin{itemize}
  \vspace{-2mm}
 \item Developed C code to control robot motion and ability to autonomously traverse a maze. 
 \end{itemize}

\section{Activities} 
 Institute of Electrical and Electronic Engineers | Member \\
 University of Iowa Powerlifting Club Treasurer (2013) | Member (Present) 
 
\section{Awards} 
 Awarded Dean’s List for Fall 2013, Fall 2014

\end{resume}
\end{document}



